---
title: "Homework 5"
author: "Fifi"
date: "November 11, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###In-line Approach
1) mpg~cyl+wt
```{r, include=TRUE}
x1<-lm(mpg~cyl+wt, data = mtcars)
summary(x1)
```
2) mpg~cyl+wt+am
```{r, include=TRUE}
x2<-lm(mpg~cyl+wt+am, data = mtcars)
summary(x2)
```
3) mpg~cyl+wt+hp+qsec
```{r, include=TRUE}
x3<-lm(mpg~cyl+wt+hp+qsec, data = mtcars)
summary(x3)
```


###for loop
```{r,include=TRUE}
varlist<-c(mpg~cyl+wt, mpg~cyl+wt+am, mpg~cyl+wt+hp+qsec)
list.output<-list()
cmts<-c('All coefficients are significant','Coefficient for am is not significant','Coefficients for wt, hp and qsec a are not significant')
j=0
for (i in varlist) {
  j=j+1
  print(i)
  lmobj<-lm(i,data = mtcars)
  print(summary(lmobj))
  print(cmts[j])
  list.output[[length(list.output)+1]]<-lmobj
}
anova(list.output[[1]],list.output[[2]])
anova(list.output[[1]],list.output[[3]])
```

The ANOVA test between 1st and 2nd model shows that the addition of 'am' variable is not significant (p>0.05). Similarly, the ANOVA test between 1st and 3rd model shows that the addition of 'hp' and 'qsec' are not significant (p>0.05). Therefore the preferred model should be the 1st model because it demonstrates a significant correlation between the dependent variables and both the independent variables. 

###Table driven
```{r,include=TRUE}
table<-read.csv(file = 'table.csv')
table.n<-nrow(table)
ind<-grep('Valiant',rownames(mtcars),ignore.case = TRUE)
comment<-c('All coefficients are significant','Coefficient for am is not significant','Coefficients for wt, hp and qsec a are not significant','All coefficients are significant','Coefficient for am is not significant','Coefficient for am is not significant')
output<-list()
for (i in 1:table.n) {
  fml<-as.formula(paste(table$response[i],'~',table$covariate[i],sep = ''))
  print(paste(table$response[i],'~',table$covariate[i],sep = ''))
  if(table$model[i]==1){
    if(table$dataset[i]==1){
    lm.obj<-lm(fml,data=mtcars)
    print(summary(lm.obj))
    output[[length(output)+1]]<-lm.obj}
    else{lm.obj<-lm(fml,data=mtcars[-ind,])
    print(summary(lm.obj))
    output[[length(output)+1]]<-lm.obj}}

  else
  {
    if(table$dataset[i]==1){
    glm.obj<-glm(fml,data=mtcars)
    print(summary(glm.obj))
    output[[length(output)+1]]<-glm.obj}
    else{glm.obj<-glm(fml,data=mtcars[-ind,])
    print(summary(glm.obj))
    output[[length(output)+1]]<-glm.obj}
  }
  print(comment[i])
}

```